Using Local PCA to Investigate Population Structure Along the Genome

### 2016-05-06 medicago/medicago_data_setup.Rmd
added manpages

>>>>

## Statistics by chromosome

We should know what the density of SNPs looks like, for choosing window sizes.
Chromosome lengths are from the VCF files.
```{r snp_density, cache=TRUE}
chrom.lens <- c( chr1=52991155, chr2=45729672, chr3=55515152, chr4=56582383, chr5=43630510, chr6=35275713, chr7=49172423, chr8=45569985, chl_Mt=124033 )
chrom.stats <- sapply( paste0("chr",1:8), function (chrom) {
            bcf.file <- file.path("data",sprintf("%s-filtered-set-2014Apr15.bcf",chrom))
            sites <- vcf_positions(bcf.file)
            spacings <- diff(sites[[chrom]])
            out <- c( nsnps = length(sites[[chrom]]),
                    nbp = chrom.lens[chrom],
                    spacing.mean = mean(spacings),
                    spacing = quantile(spacings,.05),
                    spacing = quantile(spacings,.25),
                    spacing = quantile(spacings,.50),
                    spacing = quantile(spacings,.75),
                    spacing = quantile(spacings,.95),
                    spacing.max = max(spacings,.95) )
            return(out)
        } )
floor(chrom.stats)
```
